Understanding domestic abuse - Pathways to Impact

### 2019-07-24 pathways_to_impact.tex
Anna Pathways to impact

Our pathway to impact is built upon the strong existing relationships we have with Wast Midlands Police (WMP) , and the college of policing. These existing relationships are complemented by our membership of the University of Warwick's Centre for Operational Policing Research (COPR), which provides access to an even wider established network within UK policing.

The research proposed here has been developed with direct input from officers and experts within WMP. This has allowed us to design the research questions that are relevant to current issues within WMP, and that can feed in to existing structures to accelerate the dissemination of findings, and changes in policy. To facilitate this, we have a day-to-day contact at WMP: Inspector Jenny Richards (Evidence Based Practice in Risk and Organisational Learning), and within the WMP and Crime Commissioner's Office, Alison Spence. As a result of this close collaboration, we have received support from senior levels within WMP including from Deputy Chief Constable Louisa Rolfe who is the National Police Chiefs Council lead for domestic abuse.

These relationships will enable us to work with WMP to import the insight from the research into their senior management team and also their day-to-day processes. This will be possible for each of the objectives and topics within our proposal:

@@

In addition to working with WMP, our links to the National Police Chiefs council, and collaboration with the College of Policing, provide pathways for impact across all forces. At the College of Policing (situated just a few miles from Warwick campus) we will work within the framework of the \href{https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/) and the revision of the existing DASH risk assessment tool for domestic abuse. (https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf}{Authorised Professional Practice} on domestic abuse, released in 2015. We will work initially with David Tucker, Head Crime and Criminal Justice at the College of Policing.

We will meet regularly with our contacts at WMP and the college of policing throughout the grant. This will enable us to adapt to current questions that arise during the period of the proposal. It also allows us to react quickly to any unanticipated issues that arise as a result of our findings, such as following up on unexpected results to identify underlying causes. It also ensures that there is an ongoing dialogue about the data being used, and provides an opportunity to alert the police to any data quality issues.

In the second year of the proposal we will hold a 1-day impact summit at Warwick Business School's London Shard venue. This will be funded by the Warwick Business School Impact Fund, and potentially the ESRC Impact Acceleration Account. We will host the National Police Chiefs' Council lead for Domestic Abuse, Deputy Chief Constable Louisa Rolfe (who is also at WMP), and Members of Parliament from the Home Affairs Committee domestic abuse inquiry. The summit will be a 50/50 academic / practitioner mix. We will contact, early in the project, domestic abuse charities Women's Aid, Refuge, Safe Lives, and National Centre for Domestic Abuse, and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.

In addition to the academic journal outputs, we will present the findings in a series of thought leadership pieces for dissemination across the police and third-sector contacts. We will submit these reports to the College of Police What Works database and log them on the \href{https://whatworks.college.police.uk/Research/Research-Map/Pages/Research-Map.aspx}{Research Map}.

@@

Within Lloyds Bank, we will work with Martin King, Head of Customer Vulnerability. Warwick already has a relationship with King's team in CI Stewart's work on the effects of gambling, which was completed using micro-level transaction data from millions of account holders. Key issues here are work on coercion and control, and how financial resilience affects the decision to contact the police and escape the cycle of abuse. Our day-to-day contact at Lloyds is Dr David Leake, Head of the Behavioural Insights Team. We will present the findings from all four programmes to the Lloyds Vulnerability Team in six-monthly briefings, and work to integrate insight from the research into the Lloyds environment.

>>>>

Our pathway to impact is built upon the strong existing relationships we have with Wast Midlands Police (WMP), and the College of Policing (CoP). These existing relationships are complemented by our membership of the University of Warwick's Centre for Operational Policing Research (COPR), which provides access to an even wider established network within UK policing.

The research proposed here has been developed with direct input from officers and experts within WMP. This has allowed us to design the research questions that are relevant to current issues within the WMP, and that can feed in to existing structures to accelerate the dissemination of findings, and contribute to changes in policy. To facilitate this, we have a day-to-day contact at WMP with Inspector Jenny Richards (Evidence Based Practice in Risk and Organisational Learning), and Alison Spence (Crime Commissioner's Office). As a result of this close collaboration, we have received support from senior levels within WMP including from Deputy Chief Constable Louisa Rolfe, who is the National Police Chiefs Council lead for domestic abuse.

These relationships will enable us to work with WMP to import insights generated from our the research into their senior management team, and also their day-to-day processes. This will be possible for each of the objectives and topics within our proposal:

@@

In addition to working with WMP, our links to the National Police Chiefs council, and collaboration with the CoP, provide pathways for impact across all forces. At the CoP (situated just a few miles from Warwick campus) we will work within the framework of the \href{https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/)}{Authorised Professional Practice} released in 2015, and contribute to the \href{https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf}{revision of the existing DASH risk assessment tool} for domestic abuse. We will work initially with David Tucker, Head Crime and Criminal Justice at the CoP.

We will meet regularly with our contacts at WMP and the CoP throughout the grant. This will enable us to adapt to current questions that arise during the period of the proposal. It also allows us to react quickly to any unanticipated issues that arise as a result of our findings, such as following up on unexpected results to identify underlying causes. It also ensures that there is an ongoing dialogue about the data being used, and provides an opportunity to alert the police to any data quality issues.

In the second year of the proposal, we will hold a 1-day impact summit at Warwick Business School's London Shard venue. This will be funded by the Warwick Business School Impact Fund, and potentially the ESRC Impact Acceleration Account. We will host the National Police Chiefs' Council lead for Domestic Abuse, Deputy Chief Constable Louisa Rolfe (who is also at WMP), and Members of Parliament from the Home Affairs Committee domestic abuse inquiry. The summit will be a 50/50 academic and practitioner mix. We will contact, early in the project, domestic abuse charities including Women's Aid, Refuge, Safe Lives, and National Centre for Domestic Abuse, and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.

In addition to the academic journal outputs, we will present the findings in a series of thought leadership pieces for dissemination across the police and third-sector contacts. We will submit these reports to the CoP What Works database and log them on the \href{https://whatworks.college.police.uk/Research/Research-Map/Pages/Research-Map.aspx}{Research Map}.

@@

Within Lloyds Bank, we will work with Martin King, Head of Customer Vulnerability. Warwick already has a relationship with King's team in CI Stewart's work on the effects of gambling, which was completed using micro-level transaction data from millions of account holders. Key issues here are work on coercion and control, and understanding the extent to which financial resilience affects the decision to contact the police and escape the cycle of abuse. Our day-to-day contact at Lloyds is Dr David Leake, Head of the Behavioural Insights Team. We will present the findings from all four programmes to the Lloyds Vulnerability Team in six-monthly briefings, and work to integrate insight from the research into the Lloyds environment.
